\section{Activities and tasks}

\par To implement \RCC{} with concurrent \PBFT{} instances in Nexres. Four modules are required: \emph{Client, 
Primary, Backup Replica, Total Ordering}. All modules consists of normal-case algorithms and recovery algorithms. 
The implementation of normal-case algorithms is of higher priority while the implementation of recovery algorithms 
is optinonal. Also, evaluation that help us assess \RCC{}'s performance is necessary.

\subsection{Client}

\par Clients are the generators of transaction requests. In \RCC{}, the client $\Client{}$ generates a batch 
of client transactions $T$ and send the batch to a preferred replica $\Replica{}$. $Client{}$ sets a timer 
$t_T$ after sending $T$ to $\Replica{}$ and waits for responses from $\f+1$ distinct replicas that claim 
to have committed $T$. After receving sufficient responses, $\Client{}$ counts the latency of each client 
transaction. $\Client{}$ will complain to other replicas if $\Client{}$ fails to receive $\f+1$ responses 
before $t_T$ is out.

\subsection{Primary}

\par The primary $\Primary{i}$ of instance $\Instance{i}$ is the leading role of consensus in the 
instance. After receiving a client batch $T$, $\Primary{i}$ acts as primary in \PBFT{}, and broadcast $T$ 
with instance id $i$ to other replicas.

\par If $\Primary{i}$ is detected to have faulty behavior for the $k$-th time at round $r$, then the proposals 
from $\Primary{i}$ will be ignored by other replicas until round $r + 2^k$.

\subsection{Backup Replica}

\par After receiving a proposal $T$ of instance $\Instance{i}$, a non-faulty replica $\Replica{}$ 
checks the validity of $T$ and if $T$ is proposed by the correct primary $\Primary{i}$. If $T$ is valid, 
then $\Replica{}$ participates in the \PBFT{} agreement process of $T$.

\par If $\Replica{}$ receives a complaint from client $\Client{}$, then it forwards it to the corresponding 
primary $\Primary{}$, sets a timer $t_c$, and waits for a corresponding proposal from $\Primary{}$. If $\Replica{}$ 
fails to receive a corresponding proposal before $t_c$ is out, then $\Primary{}$ is detected to have faulty behavior. 

\par If $\f+1$ distinct replicas have detected $\Primary{i}$'s faulty behavior, then $\Instance{i}$ will be temporarily 
stalled as mentioned above.

\subsection{Total Ordering}

\par Before executing committed client transactions, \RCC{} totally orders the committed transactions between different 
instances. For all committed transactions, \RCC{} executes round by round. In \RCC{} with $\m$ concurrent instances, in 
each round, \RCC{} executes transactions with increasing instance id, from the instance $\Instance{0}$ to the instance $\Instance{\m-1}$.

\subsection{Evaluation}

\par To evaluate the performance of \RCC{}, we will conduct the following experiments for \RCC{} and \PBFT{}:

\begin{enumerate}
    \item Best-case Throughput. Compare the \emph{best-case} throughput of \RCC{} and \PBFT{} of different scales.
    \item Throughput-Latency. Compare the best latency with the peak throughput of \RCC{} and \PBFT{} of different scales.
    \item Batching. Compare the \emph{best-case} throughput of \RCC{} and \PBFT{} of different batch size.
    \item Concurrency. Compare the \emph{best-case} throughput of \RCC{} of different instance numbers.
\end{enumerate}